### 2023-06-29 paper/main.tex
matlab_added

\author{\IEEEauthorblockN{Gergely Firtha}
    \IEEEauthorblockA{\textit{Dept. of Networked Systems and Services} \\
        \textit{Budapest University of Technologies and Economics}\\
        H-1111 Budapest, Hungary \\
        firtha@hit.bme.hu}
    \and
    \IEEEauthorblockN{Nara Hahn}
    \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
        \textit{name of organization (of Aff.)}\\
        City, Country \\
        email address or ORCID}
    \and
    \IEEEauthorblockN{Frank Schultz}
    \IEEEauthorblockA{\textit{Institute of Communications Engineering} \\
        \textit{University of Rostock}\\
        18059 Rostock, Germany \\
        frank.schultz@uni-rostock.de}
    \and
    \IEEEauthorblockN{Péter Fiala}
    \IEEEauthorblockA{\textit{Dept. of Networked Systems and Services} \\
        \textit{Budapest University of Technologies and Economics}\\
        H-1111 Budapest, Hungary \\
        fiala@hit.bme.hu}
}

@@

As WFS obtains the necessary driving functions from a suitable boundary integral representation of the target sound field, perfect phase correct field-reconstruction could be only achieved by employing a theoretical, continuous secondary source distribution.
In practical applications the SSD constist of discrete loudspeaker elements, resulting in secondary wavefronts additionally to the intended virtual wavefront, emerging from the individual SSD elements, termed as aliasing waves.
This spatial aliasing phenomena is perceived as the coloration of the synthesized sound field above the spatial aliasing frequency, varying with the listening position and the virtual wavefront direction, heavily degrading the quality of reproduction.

The effect of aliasing can be mitigated by restricting the synthesis to a smaller control region inside the listening area at the cost of permitting stronger aliasing artifacts outside the control region.
These anti-aliased WFS approaches are commonly referred to as Local Wave Field Synthesis (LWFS).
Conventional LWFS approaches achieve increased local synthesis accuracy by the direct spatial bandlimitation of the WFS driving functions \cite{}.
However, due to the high computational demand the real-time application of these LWFS approaches is not straightforward.

The present contribution introduces a novel LWFS approach, relying merely on the temporal bandlimitation of the SSD driving functions.
The temporal filters, defined uniquely for each SSD elements, are obtained from spatial antialiasing filters by means of an analytical spatial-to-temporal filter transformation, introduced by the current authors in a previous contribution \cite{firtha_daga}.
Similarly to other LWFS techniques, the presented approach ensures aliasing-free synthesis at a predefined listening position at the cost of temporally bandlimited sound field at other listening regions.
The results of the proposed approach are compared with a conventional LWFS approach employing direct spatial bandlimitation.

@@

It should be noted that the presented spatial-to-temporal filter transform strategy can be also interpreted as a frequency dependent spatial windowing approach:
in the aspect of antialiasing filtering SSD positions where the local wavenumber vector is higher than the Nyquist wavenumber are highly attenuated, with the window width decreasing with increasing angular frequency.
\begin{figure}[]
    \begin{overpic}[width = 1\columnwidth]{figs/equivalent_windows.png}
    \end{overpic}
    \caption{Illustration of equivalent frequency dependent window functions}
    \label{Fig:equivalent_windows}
\end{figure}
The actual shape of the spatial windows are given by the wavenumber spectrum of the spatial lowpass filter $H_x(k_s)$, rescaled in terms of the local wavenumber vector.
The set of window functions applied in the present simulation scenario are illustrated in Figure \ref{Fig:equivalent_windows}.

>>>>

\author{\IEEEauthorblockN{Gergely Firtha}
    \IEEEauthorblockA{\textit{Dept. of Networked Systems and Services} \\
        \textit{Budapest University of Technologies and Economics}\\
        H-1111 Budapest, Hungary \\
        firtha@hit.bme.hu}
    \and
    \IEEEauthorblockN{Nara Hahn}
    \IEEEauthorblockA{\textit{Institute of Sound and Vibration Research} \\
        \textit{University of Southampton}\\
        Southampton, United Kingdom \\
        nara.hahn@soton.ac.uk}
    \and
    \IEEEauthorblockN{Frank Schultz}
    \IEEEauthorblockA{\textit{Institute of Communications Engineering} \\
        \textit{University of Rostock}\\
        18059 Rostock, Germany \\
        frank.schultz@uni-rostock.de}
    \and
    \IEEEauthorblockN{Péter Fiala}
    \IEEEauthorblockA{\textit{Dept. of Networked Systems and Services} \\
        \textit{Budapest University of Technologies and Economics}\\
        H-1111 Budapest, Hungary \\
        fiala@hit.bme.hu}
}

@@

As WFS obtains the necessary driving functions from a suitable boundary integral representation of the target sound field, perfect phase correct field-reconstruction could be only achieved by employing a theoretical, continuous secondary source distribution.
In practical applications the SSD constist of discrete loudspeaker elements, resulting in secondary wavefronts additionally to the intended virtual wavefront, emerging from the individual SSD elements, termed as aliasing waves.
This spatial aliasing phenomena is perceived as the coloration of the synthesized sound field above the spatial aliasing frequency, varying with the listening position and the virtual wavefront direction, heavily degrading the quality of reproduction \cite{8371275, 8611109}.

The effect of aliasing can be mitigated by restricting the synthesis to a smaller control region inside the listening area at the cost of permitting stronger aliasing artifacts outside the control region.
These anti-aliased WFS approaches are commonly referred to as Local Wave Field Synthesis (LWFS).
Conventional LWFS approaches achieve increased local synthesis accuracy by the direct spatial bandlimitation of the WFS driving functions \cite{Winter2016-TASL, Hahn17:EUSIPCO}.
However, due to the high computational demand the real-time application of these LWFS approaches is not straightforward.

The present contribution introduces a novel LWFS approach, relying merely on the temporal bandlimitation of the SSD driving functions.
The temporal filters, defined uniquely for each SSD elements, are obtained from spatial antialiasing filters by means of an analytical spatial-to-temporal filter transformation, introduced by the current authors in a previous contribution \cite{firtha_daga2023}.
Similarly to other LWFS techniques, the presented approach ensures aliasing-free synthesis at a predefined listening position at the cost of temporally bandlimited sound field at other listening regions.
The results of the proposed approach are compared with a conventional LWFS approach employing direct spatial bandlimitation.

@@

It should be noted that in the angular frequency domain the filtered driving function is written as
\begin{equation}
    D'_t(s,\omega) = D(s,\omega) H_t(s,\omega) =  H_x\left(-k_t^P(s)\right) \, D(s,\omega),
\end{equation}
from which formulation it is apparent that in the frequency domain the presented spatial-to-temporal filter transform strategy can be also interpreted as a frequency dependent spatial windowing approach, and the frequency dependent spatial window is given by $H_x\left(-k_t^P(s)\right)$:
in the aspect of antialiasing filtering SSD positions where the local wavenumber vector is higher than the Nyquist wavenumber are highly attenuated, with the window width decreasing with increasing angular frequency.
\begin{figure}[]
    \begin{overpic}[width = 1\columnwidth]{figs/equivalent_windows.png}
    \end{overpic}
    \caption{Illustration of equivalent frequency dependent window functions}
    \label{Fig:equivalent_windows}
\end{figure}
The actual shape of the spatial windows are given by the wavenumber spectrum of the spatial lowpass filter $H_x(k_s)$, rescaled in terms of the local wavenumber vector.
The set of window functions applied in the present simulation scenario are illustrated in Figure \ref{Fig:equivalent_windows}.
